---
title: "What is a Lossrun ?"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What is a Lossrun ?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(lossrunAnalyzer)
```

## What is a lossrun?

A 'lossrun' is an insurance term for a dataset containing information about a particular insurance coverage or policy's individual claims.

**lossrunAnalyzer** supports analyzing for the following Property Casualty coverages:

+ Workers Compensation - WC
+ Automobile Liability - AL
+ General Liability - GL
+ Medical Professional Liability - MPL (Hospitals and Physicians)
+ Other Various Liability Types similar to WC, AL, and GL (i.e. property, government, etc.)

Different coverages have different types of fields in their respective lossruns which is discussed in detail in the coverages vignette.

Each row in a lossrun should correspond to a specific claim.

The following fields are typical in a lossrun:

+ Key Fields:
  - Unique Claim ID
  - Occurence ID (for claims related to a single accident that are grouped by occurrence)
  - Claimant Name
  - Other Claimant Information (Age, Gender, Tenure, etc.)
  - Policy Details

+ Dates
  - Evaluation Date of the Lossrun
  - Date of Accident / Loss
  - Date of Report
  - Close Date

+ Claim Information Fields
  - Claim Status
  - Claim Type
  - Litigation

+ Numeric Financial Fields
  - Total Unlimited Reported / Incurred
  - Total Unlimited Paid
  - Total Unlimited Reserve
  - Various Splits depending on Coverage
  - Recoveries, Subrogation, etc.
